Scikit-learn: machine learning without learning the machinery

### 2014-07-02 article.tex
wording

\paragraph{Model evaluation and parameter selection.}
%
The performance of a model measures its ability to correctly
predict new data. Because of overfitting, the \emph{train} data used to build a
model should in general not be used to also evaluate its performance, as it may often
result in overly optimistic estimates of its true prediction error.
Accordingly, the correct way to obtain an unbiased estimate is to leave out \emph{test} data,
untouched during training and used for model evaluation only.
Often a \emph{cross-validation} scheme is
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tune the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data.

>>>>

\paragraph{Model evaluation and parameter selection.}
%
The performance of a model measures its ability to correctly
predict new data. Because of overfitting, the \emph{train} data used for building
should in general not be used to also evaluate model performance, as it may often
result in overly optimistic estimates of the true prediction error of the model.
Accordingly, the correct way to obtain an unbiased estimate is to leave out \emph{test} data,
untouched during training and used for model evaluation only.
Alternatively, a \emph{cross-validation} scheme may also be
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tune the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data.
